LC-MS ^13^C Lactate Measurements

### 2022-12-19 analysis/glc6-lactate.qmd
split out dna flux preprocessing

withr::with_dir(here::here(), {
  se_raw <- tar_read(fluxes_glc6_se)
  df_drift <- tar_read(fluxes_glc6_drift)
})
```

@@

df_drift |> 
  dplyr::filter(type == "std" & metabolite == "LAC M0") |> 
  dplyr::mutate(conc = as.numeric(conc)) |> 
  ggplot() +
  aes(
    x = conc, 
    y = area
  ) +
  geom_point()
```

>>>>

withr::with_dir(here::here(), {
  se_raw <- tar_read(fluxes_glc6_se)
  df_drift <- tar_read(fluxes_glc6_drift)
  std <- tar_read(conc_std)
})
```

@@

std |> 
  filter(experiment == "substrate" & metabolite == "lactate") |> 
  pull(plots)
```
